### 2021-04-17 README.rmd
working on the readme, the badge rcmd-check was not present before

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/workflows/R-CMD-check/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JeremyGelb/geocmeans/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
